% /////////////////////////////////////////////////////////////////////////////
%  My Curriculum Vitae
%
%  Justin A. Vasel <justin.vasel@gmail.com>
%  https://www.justinvasel.com
%  4 April 2018
%
% /////////////////////////////////////////////////////////////////////////////

\documentclass[11pt]{cv}

\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true, urlcolor=NavyBlue]{hyperref}
\usepackage{amsmath}
\usepackage[spanish]{babel}
\usepackage{etaremune}

% .............................................................................
\begin{document}
\name{Justin A. Vasel}

\begin{cv}


% .............................................................................
% CONTACT
\section{Contact}
justin.vasel@gmail.com


% .............................................................................
% EDUCATION
\section{Education}

\textbf{Ph.D. in Physics}, \emph{Indiana University (IU)} \hfill \emph{Expected September 2019} \\
Thesis advisor: Mark Messier

\textbf{M.S. in Physics}, \emph{University of Minnesota Duluth (UMD)} \hfill August 2013 \\
Thesis advisor: Alec Habig

\textbf{B.S. in Physics}, \emph{University of Wisconsin--Eau Claire (UWEC)} \hfill May 2011 \\
Research advisor: Nathan Miller


% .............................................................................
% RESEARCH
\section{Research Experience}

HEP collaboration memberships: NOvA, HALO, DUNE

NuMI Off-axis $\nu_e$ Appearance experiment (NOvA)
\begin{itemize}
  \item Performed maintenance and repairs on front-end boards and other detector components
  \item Served as DAQ on-call expert for two years
  \item Served as an expert on timing system hardware and software components
  \item Designed and implemented a monitoring system for long-duration readouts
  \item Contributed to testing of supernova triggering system.
  \item Investigating NOvA's capabilities and physics reach as a supernova neutrino observatory
\end{itemize}

Helium and Lead Observatory (HALO)
\begin{itemize}
  \item Designed and currently maintain the HALO DAQ monitoring system
\end{itemize}


% .............................................................................
% TECHNICAL
\section{Technical \\ Skills}
Unix system administration \\
Basic networking: routing, subnets, firewalls \\
Computer hardware and construction \\
Electronics: basic circuit design/components, soldering, multimeter, oscilloscope \\
Language proficiency: C++, Python, Bash, \LaTeX, HTML/CSS, Javascript, PHP \\
Software proficiency: ROOT, ART, Pandas, matplotlib \\
Operating System proficiency: Linux/Unix, macOS


% .............................................................................
% HONORS & AWARDS
\section{Honors \& Awards}

Trevi\~{n}o Service Award, IU Graduate and Professional Student Organization \hfill 2014 \\
Outstanding Teaching Assistant Award, American Association of Physics Teachers \hfill 2013 \\
Outstanding Graduate Teaching Assistant Award, UMD \hfill 2013 \\
First Place, Student Research Day Poster Competition, UWEC \hfill 2011 \\
Silver Medal, University Physics Competition 2010 \hfill 2010 \\
Physics Beyond The Classroom Scholarship, UWEC \hfill 2010


% .............................................................................
% PROFESSIONAL ACTIVITIES
\section{Professional Activities}

HEP Advocacy Trip, Washington, D.C. \hfill 2017, 2018 \\
\emph{Annual trip organized by Fermilab's Users Executive Committee to advocate for continued Federal investment in high-energy physics with lawmakers on Capitol Hill.}

43$^{\text{rd}}$ SLAC Summer Institute, SLAC National Laboratory \hfill 2015 \\
\emph{Attended summer school. Theme: ``The Universe of Neutrinos''.}


% .............................................................................
% COMMUNITY SERVICE
\section{Community Service}

President, Young NOvA \hfill May 2017 --- 2018 \\
Young NOvA Rep., NOvA Institutional Board \hfill May 2016 --- 2017

Member, Search Committee for IU Vice Pres. of Research \hfill April --- June 2015

Vice President, IU Graduate and Professional \hfill May 2014 --- 2015 \\
\verb!   ! Student Organization (GPSO) \\
Chair, GPSO Student Affairs Committee \hfill May 2014 --- 2015 \\
Member, IU Bloomington Faculty Council (BFC) \hfill May 2014 --- 2015 \\
Member, IU BFC Student Affairs Committee \hfill May 2014 --- 2015 \\
Member, IU Campus Curriculum Committee \hfill May 2014 --- 2015 \\
Member, IU Student Assistance Initiative \hfill May 2014 --- 2015

Physics Representative, GPSO \hfill Sept. 2013 --- May 2014 \\
Vice Chair, GPSO Student Affairs Committee \hfill Sept. 2013 --- May 2014 \\
Member, IU BFC Research Affairs Committee \hfill Sept. 2013 --- May 2014

Graduate Student Rep., UMD Graduate Council \hfill Dec. 2012 --- Aug. 2013

Member, UMD Technology Fees Committee \hfill Sept. 2012 --- May 2013

President, UMD Society of Physics Students \hfill Dec. 2011 --- Feb. 2013

President, UW--Eau Claire Society of Physics Students \hfill May 2010 --- 2011 \\
Webmaster, UW--Eau Claire Society of Physics Students \hfill May 2008 --- 2010

Senator, Winona State University Student Senate \hfill Sept. 2006 --- May 2007
\begin{itemize}
  \item Election Committee
  \item Cultural Diversity Committee
\end{itemize}


% .............................................................................
% OUTREACH
\section{Outreach}
Judge, Northeastern Minnesota Regional Science Fair \hfill Feb. 2013 \\
Adoptee, Adopt-A-Physicist \hfill Oct. 2012 \\
Judge, Lakeview Christian Academy Science Fair \hfill Dec. 2011 \\
Volunteer, UW--Eau Claire Astronomy Day \hfill May 2011


% .............................................................................
% PAPERS: PROCEEDINGS
\section{Limited Authorship Publications}
\begin{etaremune}
  \item K. Albertsson et al., \it Machine Learning in High Energy Physics \rm \hfill 2018 \\
  \it Community White Paper, \rm \href{https://arxiv.org/abs/1807.02876}{arXiv:1807.02876}.
  \item D. Berzano et al., \it HEP Software Foundation Community White Paper \rm \hfill 2018 \\
  \it Working Group -- Training, Staffing and Careers, \rm \href{https://arxiv.org/abs/1807.02875}{arXiv:1807.02875}.
\end{etaremune}

\newpage

% .............................................................................
% PAPERS: COLLABORATION
\section{Publications From Large Collaborations}
\begin{etaremune}
  \item B. Abi et al., \it The DUNE Far Detector Interim Design Report Volume 3: \rm \hfill 2018 \\
  \it Physics, Technology and Strategies, \rm \href{https://arxiv.org/abs/1807.10340}{arXiv:1807.10340}.
  \item B. Abi et al., \it The DUNE Far Detector Interim Design Report Volume 2: \rm \hfill 2018 \\
  \it Single-Phase Module, \rm \href{https://arxiv.org/abs/1807.10327}{arXiv:1807.10327}.
  \item B. Abi et al., \it The DUNE Far Detector Interim Design Report Volume 1: \rm \hfill 2018 \\
  \it Dual-Phase Module, \rm \href{https://arxiv.org/abs/1807.10334}{arXiv:1807.10334}.
  \item M. A. Acero et al., \it New constraints on oscillation parameters from \rm \hfill 2018 \\
  \it $\nu_e$ appearance and $\nu_\mu$ disappearance in the NOvA experiment, \rm \\
  \href{https://doi.org/10.1103/PhysRevD.98.032012}{10.1103/PhysRevD.98.032012}.
  \item P. Adamson et al., \it Search for active-sterile neutrino mixing using \rm \hfill 2017 \\
  \it neutral-current interactions in NOvA, \rm \href{https://doi.org/10.1103/PhysRevD.96.072006}{10.1103/PhysRevD.96.072006}.
  \item P. Adamson et al., \it Constraints on Oscillation Parameters from $\nu_e$ \rm \hfill 2017 \\
  \it  Appearance and $\nu_\mu$ Disappearance in NOvA, \rm \href{https://doi.org/10.1103/PhysRevLett.118.231801}{10.1103/PhysRevLett.118.231801}.
  \item P. Adamson et al., \it Measurement of the neutrino mixing angle $\theta_{23}$ \rm \hfill 2017 \\
  \it in NOvA, \rm \href{https://doi.org/10.1103/PhysRevLett.118.151802}{10.1103/PhysRevLett.118.151802}.
\end{etaremune}


% .............................................................................
% PAPERS: PROCEEDINGS
\section{Conference Proceedings}
\begin{etaremune}
  \item \bf J. A. Vasel \rm et al., \it Observing the Next Galactic Supernova \rm \hfill 2017 \\
  \it with the NOvA Detectors, \rm \href{http://arxiv.org/abs/arXiv:1710.00705}{arXiv:1710.00705}.
\end{etaremune}


% .............................................................................
% TALKS: INVITED
\section{Invited Talks}
\begin{etaremune}
  \item New Perspectives 2018, Fermilab \hfill June 2018
  \item UW--Eau Claire ``Physics Thursday'' Department Seminar \hfill April 2013
\end{etaremune}


% .............................................................................
% TALKS: CONFERENCE
\section{Conference Presentations \\ \& Talks}
\begin{etaremune}
  \item Neutrino 2018, Heidelberg, Germany \hfill June 2018
  \item 50$^{\text{th}}$ Annual Users Meeting, Fermilab \hfill June 2017
  \item INT Workshop (16-61W), University of Washington \hfill Aug. 2016
  \item New Perspectives, Fermilab \hfill June 2016
  \item American Physical Society April Meeting \hfill April 2016
  \item American Physical Society April Meeting \hfill April 2013
  \item American Astronomical Society 221${^\text{st}}$ Meeting \hfill Jan. 2013
  \item American Astronomical Society 217${^\text{th}}$ Meeting \hfill Jan. 2011
\end{etaremune}


% .............................................................................
% TALKS: INTERNAL
% \section{Internal Talks}
% \begin{etaremune}
%   \item Ph.D. Candidacy Seminar \hfill May 2016
%   \item M.S. Thesis Defense, University of Minnesota Duluth \hfill Aug. 2013
%   \item UW--Eau Claire ``Physics Thursday'' Department Seminar \hfill April 2011
% \end{etaremune}


% .............................................................................
% TALKS: PUBLIC
\section{Public Talks}
\begin{etaremune}
  \item Fermilab ``Ask-A-Scientist'' lecture series \hfill Jan. 2017
  \item Chippewa Valley Astronomical Society Northwoods Starfest \hfill Aug. 2013
  \item ``Ask-A-Scientist'' lecture series, Eau Claire, WI \hfill Mar. 2013
  \item UMD Astronomy Day, Duluth, MN \hfill April 2012
\end{etaremune}


% .............................................................................

\end{cv}
\end{document}

% .............................................................................
